D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-24 ootavacuous.tex
Translation from Java to C++ and different verdicts
Suggested-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

These tests might be two decades old, but they are still quite
relevant.\footnote{
	\url{http://www.cs.umd.edu/~pugh/java/memoryModel/unifiedProposal/testcases.html}.}
This appendix evaluates them using the \co{herd7} tool and also using
manual analysis.

>>>>

These tests might be two decades old, but they are still quite
relevant.\footnote{
	\url{http://www.cs.umd.edu/~pugh/java/memoryModel/unifiedProposal/testcases.html}.}
We have translated them from Java to C++, and we evaluate them using
the \co{herd7} tool and also using manual analysis.
Please note that differences in the semantics of these two languages
result in changes in verdict for some litmus tests.
